Balsa: A Compact Line Notation Based on SMILES

### 2022-07-16 manuscript.tex
Reconciles ms production rule with text. Closes #30
Updates electron counting description to avoid double deduction. Closes #25
Ensures that stack is only defined once and only the first time its mentioned. Closes #31

Electrons are counted as follows. A molecular tree starts as a single root atom. The electron count of this atom equals the difference between proton count (atomic number) and charge. Adding a bond is a three-step process. First, a child atom is constructed with an electron count determined in the same way as the root atom. Next, the child atom and the bond are added to the molecular tree. Finally, the electron counts of each atom and the bond are updated. If parent and child are connected through a gap edge, no electrons are deducted from either atom. Should a parent atom be bound to a child bridge node, then the electron count of the referenced atom is reduced.

@@

\begin{lstlisting}
<selection> ::= "c" | "n" | "o" | "p" | "s"
\end{lstlisting}

@@

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a stack (Figure~\ref{fig:stack}). At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a \ttt{stack} (Figure~\ref{fig:stack-for-writer}). A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.

>>>>

Electrons are counted as follows. A molecular tree starts as a single root atom. The electron count of this atom equals the difference between proton count (atomic number) and charge. Adding a bond is a three-step process. First, a child atom is constructed with an electron count determined in the same way as the root atom. Next, the child atom and the bond are added to the molecular tree. Finally, the electron counts of each atom and the bond are updated. If parent and child are connected through a gap edge, no electrons are deducted from either atom. Should a parent atom be bound to a child bridge node, then the electron count of the referenced atom is not changed.

@@

\begin{lstlisting}
<selection> ::= "b" | "c" | "n" | "o" | "p" | "s"
\end{lstlisting}

@@

The presence of a branch adds some nuances over a union. The leading open parenthesis terminal (\enquote{(}) signifies that the current hub will later be re-exposed. This operation can be supported by a \textit{stack} (Figure~\ref{fig:stack}). A stack is a data structure that allows items to be added individually and removed (\enquote{popped}) in the reverse order of addition. At the start of a branch, the current hub is pushed to the stack. At the end of the branch, the stack is popped and its top value is assigned as the new hub.

@@

The presence of branches within an input data structure is encoded via the \ttt{<branch>} non-terminal. A useful tool for this purpose is a stack (Figure~\ref{fig:stack-for-writer}). A writer begins by pushing the current branch onto the stack and extending it. When a new branch is encountered, it is pushed to the stack and extended. When the branch terminates, the current branch is popped and its contents are appended to the stack's new top item.
